\documentclass{ctexart}
\author{sjy}
\usepackage{ulem}
\title{Reflection 12.7}
\date{\today}
\begin{document}
\maketitle
Another happy and maybe fulfilling weekend. Get together with old friends, have meals, fix my robot and play games. \par
Copilot is truly annoying,i don't want it to guess what I want to write, I just want to write it myself.\sout{ But it is still a good tool for me to learn English, so I will keep using it.} (that is written by copilot.fuck it!)

There are so many 超级大神 around me.Some win the first prize in coding competition and robot competition,some are taking part in kaggle competitions,and some can make use of \LaTeX~fluently.\par

I really feel stressed out.When recalling my past experience,it truly dawned on me that I may be not as excellent an may be I have lost some valuable growing opportunities.

Is this because of the huge gap between countryside and city? No. I truly have more opportunities to try,to learn and push myself to the limits,but they are all in vain maybe because of my laziness and cowardness.

Yeah,you do make some progress.Get the opportunity to go abroad,get scholarship when this semester starts.But when this semester is close to end,you find in horror
that you do not make so many real progress apart from maybe 看得过去的 grades.

You do have to change.Make workable plan,learn modeling and polish English.What is last but maybe foremost is getting a good grades in final tests.\par

Good luck in following weeks\textasciitilde\par
\end{document}